\documentclass[11pt,a4paper]{moderncv}

	\usepackage[OT1]{fontenc}
	\moderncvtheme[blue]{classic}
	\usepackage[top=1.1cm, bottom=1.1cm, left=0.5cm, right=1cm]{geometry}
	\usepackage{eurosym}
	\setlength{\hintscolumnwidth}{2.5cm}
	\firstname{Mathieu}
	\familyname{Carri\`ere}
	\title{Topological Data Analysis and Machine Learning}
	\email{mathieu.carriere3@gmail.com}
	\mobile{+1 917-941-5182}
	\extrainfo{Adress: 390 Ft Washington Ave, \\ 10033 NYC, USA \\ https://mathieucarriere.github.io/website \\ Skype: mathieu.carriere \\ French and American citizenship}
	
	\newlength\listtripleitemmaincolumnwidth

\makeatletter
\renewcommand*{\recomputecvlengths}{%
  \setlength{\quotewidth}{0.65\textwidth}%
  \setlength{\maincolumnwidth}{\textwidth-\separatorcolumnwidth-\hintscolumnwidth}%
  \setlength{\listitemmaincolumnwidth}{\maincolumnwidth-\listitemsymbolwidth}%
  \setlength{\doubleitemmaincolumnwidth}{\maincolumnwidth-\hintscolumnwidth-\separatorcolumnwidth-\separatorcolumnwidth}%
  \setlength{\doubleitemmaincolumnwidth}{0.5\doubleitemmaincolumnwidth}%
  \setlength{\listdoubleitemmaincolumnwidth}{\maincolumnwidth-\listitemsymbolwidth-\separatorcolumnwidth-\listitemsymbolwidth}%
  \setlength{\listdoubleitemmaincolumnwidth}{0.5\listdoubleitemmaincolumnwidth}%
  \setlength\listtripleitemmaincolumnwidth{.66\listdoubleitemmaincolumnwidth}%
  \renewcommand{\headwidth}{\textwidth}%
  \setlength{\parskip}{0\p@}%
}
\makeatother

\newcommand{\cvdoublecolumn}[2]{%
  \cvline{}{%
  \begin{minipage}[t]{\listdoubleitemmaincolumnwidth}#1\end{minipage}%
  \hfill%
  \begin{minipage}[t]{\listdoubleitemmaincolumnwidth}#2\end{minipage}%
 }%
}

\newcommand{\cvtriplecolumn}[3]{%
  \cvline{}{%
  \begin{minipage}[t]{\listtripleitemmaincolumnwidth}#1\end{minipage}%
  \hfill%
  \begin{minipage}[t]{\listtripleitemmaincolumnwidth}#2\end{minipage}%
  \hfill%
  \begin{minipage}[t]{\listtripleitemmaincolumnwidth}#3\end{minipage}%
 }%
}

\newcommand{\cvreference}[7]{%
  \textbf{#1}\newline% Name
  \ifthenelse{\equal{#2}{}}{}{#2\newline}%
  \ifthenelse{\equal{#3}{}}{}{#3\newline}%
  \ifthenelse{\equal{#4}{}}{}{#4\newline}%
  \ifthenelse{\equal{#5}{}}{}{#5\newline}%
  \ifthenelse{\equal{#6}{}}{}{\texttt{#6}\newline}%
  \ifthenelse{\equal{#7}{}}{}{#7}}

\begin{document}

	\maketitle

	\section{Education}
		
		\cventry{Now}{Postdoctoral fellow}{Rabadan Lab, Columbia University, New York, USA}{}{}{}

		\cventry{11/2017}{Ph.D. in Applied Mathematics and Informatics}{DataShape, Inria Saclay, Palaiseau, France}{}{}
                {\textbf{Title:} On metric and statistical properties of topological descriptors for geometric data.} %\textbf{Advisor:} Steve Oudot.}		
		
		\cventry{02/2015}{Engineering Degree}{Ecole Centrale Paris, Ch\^atenay-Malabry, France}{}{}{}
                %{\textbf{Relevant modules:} Geometric and Topological Modeling, C++ Programming, Statistics and Data Mining, Convex Optimization.}

 		\cventry{12/2014}{M.Sc. in Mathematics, Vision and Learning}{ENS Cachan, Cachan, France}{}{}{} 
                %\textbf{Relevant modules:} Probabilistic Graphical Models, Geometry and Shape Space, Computer Vision and Learning 
                %(SVM, Boosting, Random Forests, Neural Networks).}
		

	\section{Research contributions and impact}

		\cventry{}{\normalfont My research focuses on topological data analysis (TDA) and statistical machine learning (ML).
		I contributed to the analysis of topological descriptors and on the use of 
                ML kernel methods for them with appropriate kernels, signatures and metrics. 
                %I also contributed to the study of rates of convergence and confidence intervals for these representations. 
		This work resulted in several scientific articles in top conference proceedings
		and scientific journals, and has been used in different fields, like bioinformatics and computer graphics.
		I also implemented part of this work in the C++ GUDHI library}{}{}{}{} %I am also interested in applying deep learning to TDA.

	\section{Research Articles}

	\subsection{Machine Learning}

		%\cventry{}{\normalfont Local Signatures using Persistence Diagrams. M. Carrière, S. Oudot, M. Ovsjanikov}{\textit{HAL}, 2015}{}{}{}
		\cventry{-}{\normalfont Stable Topological Signatures for Points on 3D Shapes. M. Carrière, S. Oudot, M. Ovsjanikov}
			  {\textit{Proceedings of the 13th Symposium on Geometry Processing}, 2015}
                          {}{}{\small Used topological descriptors to improve accuracy in 3D point classification on the dataset of Chen et al.}

		%\cventry{}{\normalfont Structure and Stability of the 1-Dimensional Mapper. M. Carrière, S. Oudot}{\textit{Proceedings of the 32nd Symposium on Computational Geometry}, 2016}{}{}{}
		\cventry{-}{\normalfont Sliced Wasserstein Kernel for Persistence Diagrams. M. Carrière, M. Cuturi, S. Oudot}
                          {\textit{Proceedings of the 34th International Conference on Machine Learning}, 2017}
			  {}{}{\small Derived a new kernel for Persistence Diagrams improving accuracy on various datasets, such as texture images. }

		\cventry{-}{\normalfont Statistical Analysis and Parameter Selection for Mapper. M. Carrière, B. Michel, S. Oudot}
                          {\textit{Accepted for publication in Journal of Machine Learning Research}, 2017}
                          {}{}{\small Defined confidence intervals and convergence rates for the Mapper clustering algorithm.}

		\cventry{-}{\normalfont Two-Tiers Mapper: a user-friendly clustering method for global gene expression based on topology. R. Jeitziner, 
                           M. Carrière, J. Rougemont, S. Oudot, K. Hess, C. Brisken}
                          {\textit{Submitted}}
                          {}{}{\small Used the Mapper clustering algorithm for genomics.}
	

	\subsection{Metrics}	
	%\section{Submitted articles}
		\cventry{-}{\normalfont Local Equivalence and Intrinsic Metrics between Reeb graphs. M. Carrière, S. Oudot}
                          { \textit{Proceedings of the 33rd Symposium on Computational Geometry}, 2017}
                          {}{}{\small Established a local equivalence between the bottleneck and the Gromov Hausdorff distances for Reeb graphs.}

		\cventry{-}{\normalfont Structure and Stability of the 1-Dimensional Mapper. M. Carrière, S. Oudot}
                          {\textit{Journal on Foundations of Computational Mathematics}, 2017}
                          {}{}{\small Defined appropriate metrics to prove the stability of the Mapper clustering algorithm.}

                \cventry{-}{\normalfont On the Metric Distortion of Embedding Persistence Diagrams into Reproducing Kernel Hilbert Spaces. M. Carrière, U. Bauer}
                          {}
                          {}{}{\small Established negative results about the equivalence of diagram distances and RKHS metrics.}		
	
	%\section{Research Reports}


	%\section{Manuscripts}

		
	\section{Skills}
		\cventry{Languages}{\normalfont French (native), English (professional TOEFL 627/677), Spanish (B1 level)}{}{}{}{}{}
		\cventry{Code}{\normalfont C++ (proficient), Python, R, Matlab (prior experience)}{}{}{}{}{}

	\section{Grants}
		%\cventry{}{\normalfont I received two 1000\euro{} grants, one from the DAAD exchange program, and one from the STIC doctoral school, for a 2-months visit at TU Munich, Germany,
                %        in the team of Ulrich Bauer}{}{}{}{}
		%\cventry{-}{\normalfont Funding Support from ATMCS 2016}{}{}{}{}
		\cventry{-}{\normalfont Mobility Grant (1000 euros) from the DAAD exchange program}{}{}{}{}
		\cventry{-}{\normalfont Mobility Grant (1000 euros) from the STIC doctoral school}{}{}{}{}
		\cventry{-}{\normalfont Best Scientific Contribution 2017 (2nd prize -- 600 euros) from the STIC doctoral school}{}{}{}{}
 		\cventry{-}{\normalfont Funding Support (1800 dollars) from ICML 2017}{}{}{}{}
		%\cventry{-}{\normalfont Funding Support from JGA 2017}{}{}{}{}

	\section{Teaching Activities}
		\cventry{}{\normalfont I was a teaching assistant for the following courses}{}{}{}{}
		\cventry{2015--2017}{\normalfont{\textit{Topological Data Analysis,}} \normalfont{Ecole Polytechnique, Palaiseau, France}}{}{}{}{}
		\cventry{2016--2017}{\normalfont{\textit{Basics of Algorithmic and Progamming,}} \normalfont{Ecole Polytechnique, Palaiseau, France}}{}{}{}{}

	\section{Presentations for Workshops and Conferences}
		\cventry{}{\normalfont I gave presentations at the following international conferences}{}{}{}{}
		\cventry{06/2015}{\normalfont{\textit{Symposium on Geometry Processing,}} \normalfont{TU Graz, Graz, Austria}}{}{}{}{}
		\cventry{11/2015}{\normalfont{\textit{Journées de Géométrie Algorithmique,}} \normalfont{IESC, Cargèse, Corsica}}{}{}{}{}
		\cventry{12/2015}{\normalfont{\textit{Computational and Methodological Statistics,}} \normalfont{London University, London, UK}}{Invited}{}{}{}
		\cventry{04/2016}{\normalfont{\textit{Stochastic Geometry and its Applications,}} \normalfont{Université de Nantes, Nantes, France}}{Invited}{}{}{}
		%\cventry{Jul. 2016}{\normalfont{\textit{Mathematical Methods for High Dimensional Data Analysis,}} \normalfont{TU Munich, Munich, Germany}}{}{}{}{}
		\cventry{06/2016}{\normalfont{\textit{Symposium on Computational Geometry,}} \normalfont{Tufts University, Boston, USA}}{}{}{}{}
		\cventry{07/2016}{\normalfont{\textit{Applied Topology: Methods, Computation and Science,}} \normalfont{Politecnica di Torino, Torino, Italy}}{}{}{}{}
		\cventry{08/2017}{\normalfont{\textit{International Conference on Machine Learning,}} \normalfont{ICC, Sydney, Australia}}{}{}{}{}
		\cventry{09/2017}{\normalfont{\textit{France Japan Machine Learning Workshop,}} \normalfont{ENS Ulm, Paris, France}}{Invited}{}{}{}
		\cventry{10/2017}{\normalfont{\textit{Amazon Graduate Research Symposium,}} \normalfont{Amazon Meeting Center, Seattle, USA}}{Invited}{}{}{}
		\cventry{12/2017}{\normalfont{\textit{Journ\'ees de G\'eom\'etrie Algorithmique,}} \normalfont{Centre Paul Langevin, Aussois, France}}{}{}{}{}
		\cventry{08/2018}{\normalfont{\textit{TRIPODS Bootcamp on Topology and Machine Learning,}} \normalfont{ICERM, Providence, USA}}{Invited}{}{}{}

	\section{References}

\cvtriplecolumn{\cvreference{Steve Oudot}
    {DataShape team}
    {Inria Saclay}
    {91120 Palaiseau, France}
    {}
    {steve.oudot@inria.fr}
    {+33 174 854 216}
}
{\cvreference{Marco Cuturi}
    {CREST - ENSAE}
    {Université Paris-Saclay}
    {91120 Palaiseau, France}
    {}
    {marco.cuturi@ensae.fr}
    {+33 170 266 857}
}
{\cvreference{Bertrand Michel}
    {Laboratoire Jean Leray}
    {Université de Nantes}
    {92101 Nantes, France}
    {}
    {bertrand.michel@ec-nantes.fr}
    {+33 240 372 517}
}
    
\end{document}
\grid
